Rapid Georectification of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle

### 2023-08-28 paper/paper.tex

\begin{figure}[H]
    \centering
    \includegraphics{./assets/radiance.eps}
    \caption{Radiance spectrum captured for single HSI pixel.}
    \label{fig:radiance}
\end{figure}

@@

>>>>

\textbf{NOTE:} we should update the following three figures to make a single figure with the radiances/irradiance in on the left (using the left and right y-axis) and the reflectance on the right.

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/radiance.eps}
    \caption{Radiance spectrum captured for single HSI pixel.}
    \label{fig:radiance}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/solar_irradiance.eps}
    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
    \label{fig:solar-irradiance}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/reflectance_rainbow.eps}
    \caption{Resuliting reflectance spectrum.}
    \label{fig:reflectance}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/georectification.svg}
    \caption{Georectification procedure.}
    \label{fig:georectification}
\end{figure}
